---
title: "ModelOutputs"
author: "Hannah Marchi"
date: "29 9 2021"
output: html_document
---

# Bielefeld
## two covariates
```{r, message = FALSE}
library(mgcv)
```

### all buildings

```{r}
load("Workspaces/server/Original_all_all_x2_wrapper_Bielefeld.RData")
rversion
```

#### all distances
##### Glm binomial
```{r}
summary(Original_all_all_x2$modelGlmBin)
Original_all_all_x2$qaplist$zeroGlm$xbin_1[2:4]
Original_all_all_x2$qaplist$zeroGlm$xbin_2[2:4]
```

##### Glm poisson
```{r}
summary(Original_all_all_x2$modelGlmPois)
Original_all_all_x2$qaplist$countGlm$xpois_1[2:4]
Original_all_all_x2$qaplist$countGlm$xpois_2[2:4]
```

##### Gam binomial
```{r}
summary(Original_all_all_x2$modelGamBin)
Original_all_all_x2$qaplist$zeroGam[[1]][2:4]
```

##### Gam poisson
```{r}
summary(Original_all_all_x2$modelGamPois)
Original_all_all_x2$qaplist$countGam[[1]][2:4]
rm(Original_all_all_x2)
```

#### interd

##### Glm binomial
```{r}
load("Workspaces/server/Original_interd_all_x2_wrapper_Bielefeld.RData")
rversion
summary(Original_interd_all_x2$modelGlmBin)
Original_interd_all_x2$qaplist$zeroGlm$xbin_1[2:4]
Original_interd_all_x2$qaplist$zeroGlm$xbin_2[2:4]
```

##### Glm poisson
```{r}
summary(Original_interd_all_x2$modelGlmPois)
Original_interd_all_x2$qaplist$countGlm$xpois_1[2:4]
Original_interd_all_x2$qaplist$countGlm$xpois_2[2:4]
```

##### Gam binomial
```{r}
summary(Original_interd_all_x2$modelGamBin)
Original_interd_all_x2$qaplist$zeroGam[[1]][2:4]
```

##### Gam poisson
```{r}
summary(Original_interd_all_x2$modelGamPois)
Original_interd_all_x2$qaplist$countGam[[1]][2:4]
rm(Original_interd_all_x2)
```


#### inst

##### Glm binomial
```{r}
load("Workspaces/server/Original_inst_all_x2_wrapper_Bielefeld.RData")
rversion
summary(Original_inst_all_x2$modelGlmBin)
Original_inst_all_x2$qaplist$zeroGlm$xbin_1[2:4]
Original_inst_all_x2$qaplist$zeroGlm$xbin_2[2:4]
```

##### Glm poisson
```{r}
summary(Original_inst_all_x2$modelGlmPois)
Original_inst_all_x2$qaplist$countGlm$xpois_1[2:4]
Original_inst_all_x2$qaplist$countGlm$xpois_2[2:4]
```

##### Gam binomial
```{r}
summary(Original_inst_all_x2$modelGamBin)
Original_inst_all_x2$qaplist$zeroGam[[1]][2:4]
```

##### Gam poisson
```{r}
summary(Original_inst_all_x2$modelGamPois)
Original_inst_all_x2$qaplist$countGam[[1]][2:4]
rm(Original_inst_all_x2)
```




### main building

```{r}
load("Workspaces/server/Original_all_main_x2_wrapper_Bielefeld.RData")
rversion
```


#### all distances
##### Glm binomial
```{r}
summary(Original_all_main_x2$modelGlmBin)
Original_all_main_x2$qaplist$zeroGlm$xbin_1[2:4]
Original_all_main_x2$qaplist$zeroGlm$xbin_2[2:4]
```

##### Glm poisson
```{r}
summary(Original_all_main_x2$modelGlmPois)
Original_all_main_x2$qaplist$countGlm$xpois_1[2:4]
Original_all_main_x2$qaplist$countGlm$xpois_2[2:4]
```

##### Gam binomial
```{r}
summary(Original_all_main_x2$modelGamBin)
Original_all_main_x2$qaplist$zeroGam[[1]][2:4]
```

##### Gam poisson
```{r}
summary(Original_all_main_x2$modelGamPois)
Original_all_main_x2$qaplist$countGam[[1]][2:4]
rm(Original_all_main_x2)
```

#### interd

##### Glm binomial
```{r}
load("Workspaces/server/Original_interd_main_x2_wrapper_Bielefeld.RData")
rversion
summary(Original_interd_main_x2$modelGlmBin)
Original_interd_main_x2$qaplist$zeroGlm$xbin_1[2:4]
Original_interd_main_x2$qaplist$zeroGlm$xbin_2[2:4]
```

##### Glm poisson
```{r}
summary(Original_interd_main_x2$modelGlmPois)
Original_interd_main_x2$qaplist$countGlm$xpois_1[2:4]
Original_interd_main_x2$qaplist$countGlm$xpois_2[2:4]
```

##### Gam binomial
```{r}
summary(Original_interd_main_x2$modelGamBin)
Original_interd_main_x2$qaplist$zeroGam[[1]][2:4]
```

##### Gam poisson
```{r}
summary(Original_interd_main_x2$modelGamPois)
Original_interd_main_x2$qaplist$countGam[[1]][2:4]
rm(Original_interd_main_x2)
```


#### inst

##### Glm binomial
```{r}
load("Workspaces/server/Original_inst_main_x2_wrapper_Bielefeld.RData")
rversion
summary(Original_inst_main_x2$modelGlmBin)
Original_inst_main_x2$qaplist$zeroGlm$xbin_1[2:4]
Original_inst_main_x2$qaplist$zeroGlm$xbin_2[2:4]
```

##### Glm poisson
```{r}
summary(Original_inst_main_x2$modelGlmPois)
Original_inst_main_x2$qaplist$countGlm$xpois_1[2:4]
Original_inst_main_x2$qaplist$countGlm$xpois_2[2:4]
```

##### Gam binomial
```{r}
summary(Original_inst_main_x2$modelGamBin)
Original_inst_main_x2$qaplist$zeroGam[[1]][2:4]
```

##### Gam poisson
```{r}
summary(Original_inst_main_x2$modelGamPois)
Original_inst_main_x2$qaplist$countGam[[1]][2:4]
rm(Original_inst_main_x2)
```

